---
title: "STAT 218 Lab Assignment 4"
subtitle: "Week 6 Lecture 3 Lab 4"
author: 
  - "Team Member 1: NAME HERE"
  - "Team Member 2: NAME HERE"
  - "Team Member 3: NAME HERE"
  - "Team Member 4: NAME HERE "
  - "Team Member 5: NAME HERE "
date: today
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: pdf
execute:
  echo: true
---

## Lab Assignment 4

In this assignment, we will work with the several data sets. To begin with, we need `infer`package to conduct _t_ tests. Let's load that package by using `install.packages()` function.


```{r}

# Type your code here

```

After loading that package, let's use `library` function and load the data sets that we will use today.

```{r}
#| output: false
library(tidyverse)
library(infer)
library(palmerpenguins)
data("penguins") 
stream <- read_csv("Example 8.3.4.csv")
```

__NOTE:__ Please ignore `penguins_raw` data for this class and USE `penguins` for this assignment.




# One Sample _t_ test

In this case, we will use `penguins` data set.
  
__Example of a Case:__ Imagine that you are a biologist studying penguins, particularly their bill lengths. You hypothesize that the average bill length of penguins is 40 mm and you collect a random sample of 344 penguins, measure and record their bill length in mm.



__Question 1. What is the research question of this study?__


Type your answer here.


__Question 2. What type of variable do we have in this study?__


Type your answer here.


__Question 3. Please list the assumptions required for this test and check the assumption of normality for this study. Interpret the assumptions overall.__


_Random Sampling:_ Explain here.


_Independence of Observation:_ Explain here.


_Normal Distribution:_ Explain here.



```{r}
# Type your codes here to check normality by using histogram.
```

Interpret you histogram here.

- _This code is for normal quantile plot._
```{r}
ggplot(data = na.omit(penguins),
       aes(sample = bill_length_mm)) +
  geom_qq()
```



Interpret the assumptions overall and type your reasoning.


__Question 4. Conduct a one sample $t$-test to investigate whether the bill length of the penguins differs from the test value of 40 mm. Use the 5% significance level ($\alpha = 0.05$).__


__Question 4.1 Write out the null & the alternative hypotheses within the context of this study:__

Type your answer here.


__Question 4.2. Determine \($\alpha$) level (Find it within the case given above).__

Type your answer here.


__Question 4.3. Compute test statistic by running the code chuck below and explain what you see in the output.__

```{r}
t_test(penguins, response = bill_length_mm, mu = 40)

```

Type your answer here.


__Question 4.4. Draw conclusion and write a conclusion statement.__


Type your answer here.



# Independent Samples _t_ test

In this case, we will use `penguins` data set.
  
__Example of a Case:__ Now, you're curious about the difference in the body mass of penguins based on their sex. You hypothesize that body mass varies between different sexes. To test your hypothesis, you collect a random sample of 344 penguins, measure their body mass, and record their sex.


__Question 1. What is the research question of this study?__


Type your answer here.


__Question 2. What type of variables do we have in this study?__


Type your answer here.


__Question 3. Please list the assumptions required for this test and check the assumption of normality for this study. Interpret the assumptions overall.__

_Random Sampling:_ Explain here.

_Independence of Observation:_ Explain here.

_Normal Distribution:_ Explain here.


```{r}
# Type your codes here to check normality by using histogram.
```


- _This code is for normal quantile plot for both sexes._

```{r}
ggplot(data = na.omit(penguins),
       aes(sample = body_mass_g)) +
  geom_qq() +
  facet_wrap(~sex)

```



Interpret the assumptions and type your reasoning.




__Question 4. Conduct an independent samples $t$-test to investigate whether the body mass of penguins differs between different sexes. Use the 10% significance level ($\alpha = 0.10$).__


__Question 4.1 Write out the null & the alternative hypotheses within the context of this study:__

Type your answer here.


__Question 4.2. Determine \($\alpha$) level (Find it within the case given above).__

Type your answer here.


__Question 4.3. Compute test statistic by running the code chuck below and explain what you see in the output.__

```{r}
t_test(x = penguins, 
       formula = body_mass_g ~ sex, 
       order = c("male", "female"),
       alternative = "two-sided",
       conf_level = 0.90)
```



Type your answer here.


__Question 4.4. Explain what each function/argument does in this question.__

`t_test`: Type your answer here.

`formula`:Type your answer here.

`order`: Type your answer here.

`alternative`: Type your answer here.

`conf.level`: Type your answer here.


__Question 4.5. Draw conclusion and write a conclusion statement__


Type your answer here.



# Paired Samples _t_ test

__Example of a Case:__ Pollutants in a stream may accumulate or attenuate as water flows down the stream. In a study to monitor the accumulation and attenuation of fecal contamination in a stream running through cattle rangeland, monthly water specimens were collected at two locations along the stream over a period of 21 months.

The data set `stream` the total coliform count (MPN/100ml) for a water specimen.

__Question 1. What is the research question of this study?__


Type your answer here.


__Question 2. What type of variables do we have in this study?__


Type your answer here.


__Question 3. Please list the assumptions required for this test and check the assumption of normality for this study. Interpret the assumptions overall.__


_Random Sampling:_ Explain here.

_Independence of Observation:_ Explain here.

_Normal Distribution:_ Explain here.


- _This output is from a calculation of Shapiro-Wilk test. We generally use Shapiro-Wilk test for relatively smaller sample size because visuals can be misleading in smaller sample sizes. Please interpret Shapiro-Wilk $p$-value._


	Shapiro-Wilk normality test

data:  stream$Difference
W = 0.9641, p-value = 0.6022



Type your answer here.


__Question 4. Perform a paired samples $t$-test to assess whether the mean total coliform count is consistent across the two locations. Use the 5% significance level ($\alpha = 0.05$).__


Type your answer here.



__Question 4.1 Write out the null & the alternative hypotheses within the context of this study:__

Type your answer here.


__Question 4.2. Determine \($\alpha$) level (Find it within the case given above).__

Type your answer here.


__Question 4.3. Compute test statistic by running the code chuck below and explain what you see in the output.__

```{r}
t_test(x = stream, 
       formula = coliform_count ~ location, 
       order = c("upstream", "downstream"),
       alternative = "two-sided",
       paired = TRUE)
```


Type your answer here.


__Question 4.4: What is the difference between the two `t_test` functions in independent samples t test and paired samples t test?__


Type your answer here.


__Question 4.5. Draw conclusion and write a conclusion statement__


Type your answer here.






