---
title: "STAT 218 Final Project"
author: 
  - "Team Member 1: NAME HERE"
  - "Team Member 2: NAME HERE"
  - "Team Member 3: NAME HERE"
  - "Team Member 4: NAME HERE"
  - "Team Member 5: NAME HERE"
date: today
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: pdf
execute:
  echo: true
---



__Directions:__ In this project, you will apply various statistical procedures covered in our course. Ensure to load the necessary R packages, including 'openintro' and 'tidyverse', render the `library()` functions.

This code chunk below indicates how to load your data. If you use an OpenIntro data set, simply use `data()` function to load your data. If your data set is coming from any website as a .csv file, use `read_csv()` function to load it.Keep in mind that you can use multiple data sets as for this project (please do not try to merge them in a single file).


```{r}
# Load necessary library functions here
# data(datasetname) OR
# midtermdata <- read_csv("data-set-name.csv")
```


# Part 1: Getting to Know Your Data Set

__Question 1: Use the `glimpse()` function to introduce your data set(s). Write a short paragraph explaining key aspects.__

```{r}

# Type your codes here

```

Type your answer here.


__Question 2: Determine the number of variables and cases in the data set(s).__

```{r}

# Type your codes here

```

Type your answer here.


__Question 3: Identify the types of variables in the data set (numeric or categorical).__


Type your answer here.


__Question 4: Visualize your numeric variables that you will use in this project and DESCRIBE what you see.__

```{r}

# Type your codes here

```

Type your answer here.



__Question 5: Visualize your categorical variables that you will use in this project and DESCRIBE what you see.__

```{r}

# Type your codes here

```

Type your answer here.


__Question 6: Identify and explain the handling of any outliers in your dataset, detailing whether they were removed and the rationale behind this decision.__


```{r}

# Type your codes here

```

Type your answer here.


# Part 2: Statistical Inference


In this section, you'll perform inferential statistics tests using your data set.




## The Chi-Square Test for Independence

__Directions:__ In this section, you are expected to write a case study based on your data set. Choose TWO categorical variables (with at least 2 CATEGORIES) conduct The Chi-Square Test for Independence. Show your work.


__Question 7.1. Introduce your case here.__



Type your answer here.


__Question 7.2. What is the research question of this study?__


Type your answer here.


__Question 7.3. What type of variables do we have in this study?__


Type your answer here.


__Question 7.4. Please list the assumptions required for this test.__

List the assumptions here.



__Directions for Question 5:__ Use a Chi-Square Test for Independence test to investigate your research hypothesis. Answer the questions given below. Show your work.


__Question 7.5.1 Write out the null and the alternative hypotheses:__

Type your answer here.



__Question 7.5.2. Calculate Chi-square statistic and find the p-value and explain what you see in the output.__

```{r}

# Type your codes here

```


Type your answer here.


__Question 7.5.3. Explain what each function/argument does in this question.__


Type your answer here.



__Question 7.5.4.Compute expected counts for each cell. Interpret the assumptions overall that you listed in Question 7.3.__


```{r}

# Type your codes here

```


Type your answer here.


__Question 7.5.5. Draw a conclusion and write a conclusion statement.__


Type your answer here.


__Question 7.5.6. Describe the population to which you would feel comfortable generalizing the results of this study.__


Type your answer here.


__Question 7.5.7. Were the experimental/observational units in the study randomly assigned or randomly sampled? How does this affect the scope of conclusion that you can draw? Can you make a causal conclusion, why or why not?__


Type your answer here.



__Question 7.5.8. Looking back: Did anything about the design and conclusions of this study concern you? In particular, are there things that could have been done to give a better chance finding strong evidence against the null hypothesis? Issues you may want to critique include:__

- Any mismatch between the research question and the study design   
- How the experimental/observational units were selected   
- How the treatments were assigned to the experimental units (if this is an experiment)   
- How the measurements were recorded   
- The number of experimental/observational units in the study   
- Whether what we observed is of practical value



Types your answer here.


__Question 7.5.9. Looking ahead: What should the researchers’ next steps be to fix the limitations or build on this knowledge?__


Types your answer here.



## One Way ANOVA

__Direction:__ Write a case study based on your data set. Choose a numeric variable and one categorical variable (The categorical variable should be preferably more than 2 categories) conduct One Way ANOVA. Show your work.


__Question 8.1. Introduce your case here.__


Type your answer here.


__Question 8.2. What is the research question of this study?__


Type your answer here.


__Question 8.3. What type of variables do we have in this study?__


Type your answer here.


__Question 8.4. List the assumptions required for this test and check the assumptions for this study. Interpret the assumptions overall.__

List the assumptions here and explain them.


```{r}
# Type your codes here to check assumptions
```


Interpret the assumptions and type your reasoning.



__Directions for Question 5:__ Conduct a One Way ANOVA to investigate your research hypothesis. Answer the questions given below. Show your work.


__Question 8.5.1 Write out the null and alternative hypotheses, in the context of this study.__


Type your answer here.



__Question 8.5.2. Generate an ANOVA Table and explain what you see in the output.__


```{r}

# Type your codes here

```


Type your answer here.


__Question 8.5.3. If your results imply a pairwise comparison, conduct your pairwise comparison here and summarize the output.__


```{r}

# Type your codes here

```


Type your answer here.

__Question 8.5.4. Based on your analysis, draw a conclusion regarding the observed patterns or effects. Summarize your findings by providing a conclusion statement that succinctly communicates the key results of your study. Additionally, use the `summarize()` function to create a table that presents the mean values and standard deviation values for each group involved in your analysis.__


Type your answer here.



__Question 8.5.5. Describe the population to which you would feel comfortable generalizing the results of this study.__


Type your answer here.


__Question 8.5.6. Were the experimental/observational units in the study randomly assigned or randomly sampled? How does this affect the scope of conclusion that you can draw? Can you make a causal conclusion, why or why not?__


Type your answer here.



__Question 8.5.7. Looking back: Did anything about the design and conclusions of this study concern you? In particular, are there things that could have been done to give a better chance finding strong evidence against the null hypothesis? Issues you may want to critique include:__

- Any mismatch between the research question and the study design   
- How the experimental/observational units were selected   
- How the treatments were assigned to the experimental units (if this is an experiment)   
- How the measurements were recorded   
- The number of experimental/observational units in the study   
- Whether what we observed is of practical value



Types your answer here.


__Question 8.5.8. Looking ahead: What should the researchers’ next steps be to fix the limitations or build on this knowledge?__


Types your answer here.




## Two Way ANOVA

__Directions:__ Write a case study based on your data set. Choose a numeric variable and two categorical variables (one of the categorical variables should be more than 2 categories) conduct Two Way ANOVA. Show your work.


__Question 9.1. Introduce your case here.__


Type your answer here.


__Question 9.2. What is the research question of this study?__


Type your answer here.


__Question 9.3. What type of variables do we have in this study?__


Type your answer here.


__Question 9.4. List the assumptions required for this test and check the assumptions for this study. Interpret the assumptions overall.__

List the assumptions here and explain them.


```{r}
# Type your codes here to check assumptions
```


Interpret the assumptions and type your reasoning.



__Directions for Question 9.5:__ Conduct a Two Way ANOVA to investigate your research hypothesis. Answer the questions given below. Show your work.


__Question 9.5.1 Write out the null and alternative hypotheses in words, in the context of this study.__

Type your answer here.


__Question 9.5.2. Determine the \($\alpha$) level.__

Type your answer here.


__Question 9.5.3. Generate an ANOVA Table and explain what you see in the output.__


```{r}

# Type your codes here

```


Type your answer here.


__Question 9.5.4. Analyzing Interaction and Main Effects: In your statistical analysis, evaluate the presence of interaction effects. If an interaction effect is observed, proceed to conduct a post-hoc analysis. On the other hand, if no interaction effect is identified, shift the focus to the main effects. If any of the main effects are statistically significant, perform a post-hoc analysis for those effects. Provide a comprehensive explanation of the outputs obtained during these analyses.__

```{r}

# Type your codes here

```


Type your answer here.


__Question 9.5.5.Based on your analysis, draw a conclusion regarding the observed patterns or effects. Summarize your findings by providing a conclusion statement that succinctly communicates the key results of your study. Additionally, use the `summarize()` function to create a table that presents the mean values and standard deviation values for each group involved in your analysis.__


Type your answer here.


__Question 9.5.6. Describe the population to which you would feel comfortable generalizing the results of this study.__


Type your answer here.


__Question 9.5.7. Were the experimental/observational units in the study randomly assigned or randomly sampled? How does this affect the scope of conclusion that you can draw? Can you make a causal conclusion, why or why not?__


Type your answer here.



__Question 9.5.8. Looking back: Did anything about the design and conclusions of this study concern you? In particular, are there things that could have been done to give a better chance finding strong evidence against the null hypothesis? Issues you may want to critique include:__

- Any mismatch between the research question and the study design   
- How the experimental/observational units were selected   
- How the treatments were assigned to the experimental units (if this is an experiment)   
- How the measurements were recorded   
- The number of experimental/observational units in the study   
- Whether what we observed is of practical value




Types your answer here.


__Question 9.5.9. Looking ahead: What should the researchers’ next steps be to fix the limitations or build on this knowledge?__


Types your answer here.




## Least Squares Regression

Write a case study based on your data set. Choose 2 numeric variables conduct bivariate regression to model the relationship between these two variables. Show your work.


__Question 10.1. Introduce your case here.__


Type your answer here.


__Question 10.2. What is the research question of this study?__


Type your answer here.


__Question 10.3. What type of variable do we have in this study?__


Type your answer here.


__Question 10.4. List the assumptions required for this test.__

List the assumptions here and explain them.



__Directions for Question 10.5.__ Conduct a least squares regression to investigate your research question. Answer the questions given below. Show your work.


__Question 10.5.1 Write out the null & the alternative hypotheses:__


Type your answer here.


__Question 10.5.2. Fit a least squares regression model and explain what you see in the output.__


```{r}

# Type your codes here

```


Type your answer here.



__Question 10.5.3. Go back to the assumptions. Check the assumptions for this study and interpret the assumptions overall.__

```{r}
# Type your codes here to check assumptions
```


Interpret the assumptions and type your reasoning.



__Question 10.5.4. Based on your analysis, draw a conclusion. Summarize your findings by providing a conclusion statement that succinctly communicates the key results of your study.__


Type your answer here.

__Question 10.5.5. Describe the population to which you would feel comfortable generalizing the results of this study.__


Type your answer here.


__Question 10.5.6. Were the experimental/observational units in the study randomly assigned or randomly sampled? How does this affect the scope of conclusion that you can draw? Can you make a causal conclusion, why or why not?__


Type your answer here.



__Question 10.5.7. Looking back: Did anything about the design and conclusions of this study concern you? In particular, are there things that could have been done to give a better chance finding strong evidence against the null hypothesis? Issues you may want to critique include:__

- Any mismatch between the research question and the study design   
- How the experimental/observational units were selected   
- How the treatments were assigned to the experimental units (if this is an experiment)   
- How the measurements were recorded   
- The number of experimental/observational units in the study   
- Whether what we observed is of practical value




Types your answer here.


__Question 10.5.8. Looking ahead: What should the researchers’ next steps be to fix the limitations or build on this knowledge?__


Types your answer here.



