---
title: "Two-Way ANOVA Application"
subtitle: "STAT 218 - Week 9, Lecture 2 Lab 9"
date: 2024-03-12
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: 
  revealjs:
      theme: slide-style.scss
      slide-number: true
      chalkboard: true
      incremental: true
---



# Two-Way ANOVA in R

## Let's Load Data Set


```{r}
#| echo: true
#| output: true

library(palmerpenguins)
library(tidyverse)
data(penguins)
glimpse(penguins)
```

## 
### A Note for Assumption Checking

```{r}
#| echo: true
#| output: true

na.omit(penguins) |> 
ggplot(aes(x = bill_length_mm, fill = factor(sex))) +
geom_histogram(binwidth = 1) +
facet_grid(sex ~ species, scales = "free") +
theme_minimal()
```

## 
### A Note for Assumption Checking

```{r}
#| echo: true
#| output: true
na.omit(penguins) |> 
  group_by(sex:species) |> 
summarize(mean_bill_length = mean(bill_length_mm), sd_bill_length = sd(bill_length_mm))
```

## 
### A Note for Assumption Checking

```{r}
#| echo: true
#| output: true
na.omit(penguins) |> 
group_by(sex:species) |> 
summarize(sd_bill_length = sd(bill_length_mm)) |> 
summarize(ratio_max_min_sd = max(sd_bill_length) / min(sd_bill_length))
```


## Two-Way ANOVA Function

```{r}
#| echo: true
#| output: true
two.way <- aov(bill_length_mm ~ sex + species + sex*species, data = penguins)
summary(two.way)
```

## Main Effect 1
```{r}
#| echo: true
#| output: true

pairwise.t.test(penguins$bill_length_mm, penguins$species, p.adj = "bonf")
```

## Main Effect 2

```{r}
#| echo: true
#| output: true

pairwise.t.test(penguins$bill_length_mm, penguins$sex, p.adj = "bonf")
```


## Interaction Effect

```{r}
#| echo: true
#| output: true

TukeyHSD(two.way, which = "sex:species")
```


## An Important Note
::: {style="font-size: 28px"}
- When interactions are present, the main effects of factors don’t have their usual interpretations. 
    - Because of this, we usually test for the presence of interactions first. 
      - __If interactions are present__, then we often stop the analysis at this stage and examine interaction effects. 
      - __If no evidence for an interaction effect is found__ (i.e., if we do not reject $H_0$), then we proceed
to testing the main effects of the individual factors. 

- So in this example, we ignored Main Effect 1 & Main Effect 2 and examine the Interaction Effect!
:::