---
title: "Chapter 4: The Normal Distribution"
subtitle: "STAT 218 - Week 3, Lecture 2"
date: "2024-01-23"
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: 
  revealjs:
      theme: slide-style.scss
      slide-number: true
      chalkboard: true
      incremental: true
---



## Notations

We will use some notations for important parameters and statistics as follows:

::: fragment

::: callout-important

__Population Mean:__ $\mu$  
__Sample Mean:__ $\bar{y}$  

<br>

__Population Standard Deviation:__ $\sigma$   
__Sample Standard Deviation:__ $s$

:::
:::


## Introduction to Normal Curves - I
::: {style="text-align: left; font-size: 28px"}

- We can think of normal curves as a smooth approximation to a histogram based on a sample of _$Y$_ values.
- We can describe the population distribution of a quantitative variable _$Y$_ by
  - calculating its mean $\mu$ and its standard deviation $\sigma$ AND
  - using a _density curve_ 
    - __density curve:__ relative frequencies as areas under the curve.

- Let's have a look at __Example 4.1.2__ in our book.

:::

## Introduction to Normal Curves - II

::: {style="text-align: left; font-size: 28px"}
- There is no one single normal curve but many normal curves
  - each normal curve has its own mean $\mu$ and its standard deviation $\sigma$

::: fragment
::: {style="fig-align: center; font-size: 28px"}

```{r, echo=FALSE}
# Generate data for three normal distributions
x <- seq(-4, 4, length.out = 100)
y1 <- dnorm(x, mean = 0, sd = 0.75)
y2 <- dnorm(x, mean = 1, sd = 0.85)
y3 <- dnorm(x, mean = -1, sd = 1.00)

# Plotting the normal curves
plot(x, y1, type = "l", col = "blue", lwd = 2, ylab = "Density", xlab = "Values", main = "Three Normal Curves")
lines(x, y2, col = "red", lwd = 2)
lines(x, y3, col = "green", lwd = 2)

# Adding legend
legend("topright", legend = c(expression(paste("Mean = ", mu, " = 0, ", sigma, " = 0.75")),
                              expression(paste("Mean = ", mu, " = 1, ", sigma, " = 0.85")),
                              expression(paste("Mean = ", mu, " = -1, ", sigma, " = 1.00"))), 
       col = c("blue", "red", "green"), lwd = 2)
```
:::
:::
:::

##
### Normal Curves, Continuous Variables and Probability

- If a numeric variable has a continuous distribution, we can find probabilities by using the __density curve__ for that variable.
  - For that continuous variable, the probability would be equivalent to a specific area under the density curve.
    - The area under a normal curve is always equals to 1.
      - Why?

##
#### Let's Meet with Standard Normal Distribution

```{r, echo=FALSE, out.width='600px', out.height='300px', fig.align='center'}

# Generate data for standard normal distribution
x <- seq(-3, 3, length.out = 100)
y <- dnorm(x, mean = 0, sd = 1)

# Plotting the standard normal curve
plot(x, y, type = "l", col = "maroon", lwd = 2, ylab = "Density", xlab = "Values", main = "Standard Normal Distribution")

# Customizing x-axis intervals
axis(1, at = c(-3, -2, -1, 0, 1, 2, 3), labels = c(-3, -2, -1, 0, 1, 2, 3))

```

::: fragment
:::{.callout-tip title="Standardization Formula"}
::: {style="text-align: center; font-size: 24px"}

$Z$ = ($Y$ - $\mu$) / $\sigma$

:::
:::
:::


##
### Let's See Examples 

- Please refer Example 4.1.2 and 4.3.1 from our course textbook.  

::: fragment
:::{.callout-tip title="Review 2 - Quiz"}
::: {style="text-align: center; font-size: 24px"}

See the ungraded Review 2 Quiz on Canvas (Module Week 3). 

:::
:::
:::

## References
::: {style="text-align: left; font-size: 14px"}

Samuels, M. L., Witmer, J. A., & Schaffner, A. A. (2003). Statistics for the life sciences (Vol. 4). Upper Saddle River, NJ: Prentice Hall.

:::
