---
title: " Correlation and Least Squares Regression Worksheet"
subtitle: "Week 9 Lecture 2 Lab 07"
author: " YOUR NAME HERE"
date: today
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: pdf
execute:
  echo: true
---


# Correlation


__Direction:__ This is your worksheet. PLEASE DO NOT SUBMIT THIS AS A LAB ASSIGNMENT!


Please run the code chunk below and load your data set as well as utilizing `library()` functions that you need.


```{r}
#| warning: false
library(openintro)
library(tidyverse)
data("babies")
glimpse(babies)

```


__Question 1: Please explain what you see in this dataset.__



## Calculate Correlation Coefficient



__Question 2: Please run the code chunk below and comment on the correlation coefficient.__


```{r}
cor(babies$gestation, babies$bwt, use = "na.or.complete")
```


## Outliers

Explain briefly here what an outlier is.





__Question 3: Let’s examine scatterplot to look for potential outliers. Do we have potential outliers in this scatterplot?__ 


```{r}
ggplot(na.omit(babies), aes(x = gestation, y = bwt)) +
  geom_point() +
  labs(x = "Gestation", y = "Birth Weight")
```





## Scatterplot - 1

We see two outliers on the left-hand side of the scatterplot. Let’s find them and remove these outliers. (Run the code chunk below.)


```{r}
babies <- babies %>%
  filter(case != 261 & case != 870 & case !=979) # this removes three outliers whose case numbers are 261, 870 & 979
```

Type your lecture notes here.



__Question 4: Let’s check the correlation coefficient and scatterplot again. Interpret the outputs.__


```{r}
cor(babies$gestation, babies$bwt, use = "na.or.complete")
```



```{r}
ggplot(na.omit(babies), aes(x = gestation, y = bwt)) +
  geom_point() +
  labs(x = "Gestation", y = "Birth Weight")
```

__Question 5: Do we have potential outliers in this scatterplot given above?__ 





## Scatterplot - 2


We see some outliers on the right-hand side of the scatterplot. Let’s remove those outliers.

```{r}
babies <- babies %>%
  filter(case != 1173 & case != 11 & case != 1200 & case != 153 & case != 762 & case != 970 & case != 241 & case != 254  & case != 1003 & case != 461  & case != 1045 & case != 1220)
```


__Question 6: Let’s check the correlation coefficient and scatterplot again. Interpret the outputs.__


```{r}
cor(babies$gestation, babies$bwt, use = "na.or.complete")
```

```{r}
ggplot(na.omit(babies), aes(x = gestation, y = bwt)) +
  geom_point() +
  labs(x = "Gestation", y = "Birth Weight")
```


__Question 7. Compare 3 correlation coefficients and 3 scatterplots. Interpret the potential outliers in terms of being leverage points / influential points.__

Type your answer here.


__Question 8. What is your final conclusion? Do you delete those outliers or not? Explain your reasoning.__

# Bivariate Regression

## Case of this Lab

__Understanding Birth Weight and Gestation: A Least Squares Regression Analysis__

In the area of prenatal care and childbirth, understanding the relationship between gestation period and birth weight is crucial. We often speculate about how the duration of pregnancy might be related with the weight of a newborn.

In the `babies` dataset, each observation includes information about gestation period and birth weight. We want to investigate if there’s a linear relationship between these two variables.


## Steps for Conducting Hypothesis Testing for This Test

### Step 1. Formulate Hypotheses

__Question 9. Write out the null & the alternative hypothesis in words, in the context of this study:__

Type here.


### Step 2. Generate Your Model


__Question 10. Run the code chunk below and explain what each argument does in this function.__

```{r}
# data(babies) # if you decided to keep the outliers, reload the dataset again. 
fit <- lm(babies$bwt ~ babies$gestation)
summary(fit)
```

__Question 11. Check the conditions/assumptions for this study and interpret these assumptions overall.__


### Step 3.1 Checking Conditions/Assumptions 


__Linearity with Scatterplot__


```{r}
ggplot(na.omit(babies), aes(x = gestation, y = bwt)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(title = "Scatterplot with Best-Fit Line",
       x = "Gestation",
       y = "Birth Weight")
```


__Linearity with Residuals Plot__


```{r}
# get list of residuals  
res <- resid(fit) 
res.stdres <- rstandard(fit) # standardized residuals

# produce residual vs. fitted plot 
ggplot(data.frame(fitted = fitted(fit), stdres = res.stdres), 
       aes(x = fitted, y = stdres)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "solid", color = "red") +
  labs(title = "Fitted Values vs. Standardized Residuals",
       x = "Fitted Values",
       y = "Standardized Residuals") +
  theme_minimal()
```



Type your interpretation here.


### Step 3.2. Checking Conditions/Assumptions - Normality


```{r}
# create Q-Q plot for residuals 
qqnorm(res.stdres) # by using standardized residuals
  
# add a straight diagonal line to the plot 
qqline(res.stdres)
```


Type your interpretation here.


### Step 3.3. Checking Conditions/Assumptions - Homoscedasticity


```{r}
# get list of residuals  
res <- resid(fit) 
res.stdres <- rstandard(fit) # standardized residuals

# produce residual vs. fitted plot 
ggplot(data.frame(fitted = fitted(fit), stdres = res.stdres), 
       aes(x = fitted, y = stdres)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "solid", color = "red") +  # Add a horizontal line at 0
  labs(title = "Fitted Values vs. Standardized Residuals",
       x = "Fitted Values",
       y = "Standardized Residuals")
```


Type your interpretation here.



### Draw conclusion

__Question 12. Re-run the code chunk below. Interpret Estimate, p-value of the slope, and Adjusted R-Squared.__


```{r}
fit <- lm(babies$bwt ~ babies$gestation)
summary(fit)
```



__Conclusion Statement:__


__Question 13. Type the regression equation and interpret the slope.__