---
title: "Midterm Project Workflow"
subtitle: "STAT 218 - Week 6, Lecture 1"
date: today
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: 
  revealjs:
      theme: slide-style.scss
      slide-number: true
      chalkboard: true
      incremental: true
---

# Midterm Project Guideline

## The aim of the project
::: {style="font-size: 28px"}

- The overarching goal of the projects in this course is to empower life science students by cultivating a profound <a href="https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5002400/" target="_blank"> sense of agency</a>. 
- This involves 
  - actively engaging with the learning process, 
  - making informed decisions, and 
  - taking ownership of your academic journey. 

- Through the selection of your unique data set, you will have the opportunity to construct 
  - a personalized case study, 
  - formulate research questions, 
  - employ diverse statistical procedures, and 
  - effectively communicate your findings. 

:::

## Important Deadlines

::: {style="font-size: 28px"}

- Your midterm project deadline is extended to __Feb 29__, but you can upload earlier if you'd like (please refresh your course webpage).

- **Important Deadlines:**
  - Choosing a Dataset __(due: Feb 18)__
  - Determining Variables __(due: Feb 20)__
  - Meeting with Dr. Demirci __at least once__, preferably during office hours (by appointment between __Feb 19- Feb 28)__
  - Uploading the midterm project __(due: Feb 29)__

:::


# Workflow of This Week

##
#### Choosing Your Data Set for the Midterm Project - I

::: {style="font-size: 28px"}

- For the midterm project, you will select your own dataset from [OpenIntro Data Sets](https://www.openintro.org/data/) or another suitable source. 

- If your group members share the same major, it's recommended to choose a dataset related to your field of study.

::: fragment
:::{.callout-important}
You should decide on your dataset this week and **upload it to Canvas** by Feb 18.

### STEPS TO DECIDE YOUR DATA SET

- Select a data set from either:
  - [OpenIntro Data Sets](https://www.openintro.org/data/)
  - Anywhere else on the web (but it might require more data wrangling). Some examples include:
    - [United States Environmental Protection Agency](https://www.epa.gov/data)
    - [U.S. Government's Open Data](https://data.gov/)
    - [Gapminder](https://www.gapminder.org/data/)
:::
:::
:::

## 
#### Choosing Your Data Set for the Midterm Project - II

::: {style="font-size: 27px"}

**Follow these steps FOR THIS WEEK (DUE FEB 18)**.

::: fragment
```{r}
#| echo: true
#| eval: false

library(tidyverse)
library(openintro)
data(datasetname) # Put your dataset name here
glimpse(datasetname) # Put your dataset name here
```
:::

::: fragment
If your data is coming from anywhere else on the web:

- Download your data as a CSV file.
- Load your data as follows:
:::

::: fragment
```{r}
#| echo: true
#| eval: false

library(tidyverse)
library(openintro)
midtermdata <- read_csv("data-set-name.csv")
```
:::


**UPLOAD THIS PART OF YOUR PROJECT BY THE END OF THIS WEEK!**
:::

## Choosing Your Variables

::: {style="font-size: 28px"}

<br>

Consider the following criteria while selecting your data set:

- Include **at least** 2 Numeric Variables.
- Have **at least** 2 Categorical Variables with only 2 groups each.
- Include **at least** 1 Categorical Variable with more than 3 groups.
:::