---
title: "STAT 218 Winter 2024 Midterm Project"
author: 
  - "Team Member 1: NAME HERE"
  - "Team Member 2: NAME HERE"
  - "Team Member 3: NAME HERE"
  - "Team Member 4: NAME HERE"
  - "Team Member 5: NAME HERE"
format: pdf
execute:
  echo: true
---


```{r}
#| message: false
#| warning: false
library(tidyverse)
library(openintro)
library(infer)
```



__Directions:__ In this project, you will apply various statistical procedures covered in our course. Ensure to load the necessary R packages, including 'openintro' and 'tidyverse', render the `library()` function given above.

This code chunk below indicates how to load your data. If you use an OpenIntro data set, simply use `data()` function to load your data. If your data set is coming from any website as a .csv file, use `read_csv()` function to load it. Keep in mind that I provide a data set for paired samples _t_-test. Do not forget to load that data set too.


```{r}
# Load your midterm data set here!
```


# Part 1: Getting to Know Your Data Set

__Question 1: Use the `glimpse()` function to introduce your data set(s). Write a short paragraph explaining key aspects of your data set(s).__

```{r}

# Type your codes here.

```

Type your answer here.


__Question 2: Determine the number of variables and cases in the data set(s).__

```{r}

# Type your codes here

```

Type your answer here.


__Question 3: Identify the types of variables in the data set(s) (nominal, ordinal, discrete, and continuous).__


Type your answer here.


__Question 4: Choose a numeric variable and visualize its distribution. Describe the graph.__

```{r}

# Type your codes here

```

Type your answer here.



__Question 5: Choose a categorical variable and create a visualization. Describe the graph.__

```{r}

# Type your codes here

```

Type your answer here.


__Question 6: Use the geom_boxplot() function to plot a graph showing the relationship between a single numerical and single categorical variable. Describe the graph and comment on IQRs, medians, and potential outliers.__

```{r}

# Type your codes here

```

Type your answer here.


# Part 2: Statistical Inference


In this section, you'll perform several inferential statistics tests using your data set(s).


## One Sample $t$-test


__In this section, you are expected to write a case study based on your data set. In other words, choose a numeric variable and conduct a One Sample $t$-test. Show your work.__

__Question 7.1:Introduce your case here.__

Type your case here.


__Question 7.2: What is the research question of this study?__


Type your answer here.


__Question 7.3: What type of variable do we have in this study?__


Type your answer here.


__Question 7.4: List the assumptions required for this test and check the assumption of normality for this study. Interpret the assumptions overall.__

- __Random Sampling:__ Explain here.

- __Independence of Observation:__ Explain here.

- __Normal Distribution:__ Explain here.


```{r}

# Type your codes here to check normality.

```

Interpret your outputs here.



__Question 7.5. Use a one sample $t$-test to investigate your research hypothesis. Answer the questions given below. Show your work.__


__Question 7.5.1 Write out the null and alternative hypotheses in words, in the context of this study.__

Type your answer here.


__Question 7.5.2. Determine the \($\alpha$) level.__

Type your answer here.


__Question 7.5.3. Calculate the t-statistic and explain what you see in the output.__

```{r}

# Type your codes here

```

Type your answer here.


__Question 7.5.4. Draw a conclusion and write a conclusion statement.__


Type your answer here.



## Independent Samples _t_ test

__In this section, you are expected to write a case study based on your data set. Choose a numeric variable and a categorical variable (with 2 CATEGORIES) conduct Independent Samples $t$-test. Use 90% Confidence Interval. Show your work.__



__Question 8.1:Type your case here.__

Type your case here

__Question 8.2. What is the research question of this study?__


Type your answer here.


__Question 8.3. What type of variables do we have in this study?__


Type your answer here.


__Question 8.4. List the assumptions required for this test and check the assumption of normality for this study. Interpret the assumptions overall.__

_Random Sampling:_ Explain here.

_Independence of Observation:_ Explain here.

_Normal Distribution:_ Explain here.


```{r}
# Type your codes here to check normality
```



Interpret the assumptions and type your reasoning.


__Question 8.5. Use an independent samples $t$-test to investigate your research hypothesis. Answer the questions given below. Show your work.____


__Question 8.5.1 Write out the null and the alternative hypothesis in words, in the context of this study:__

Type your answer here.


__Question 8.5.2. Determine the \($\alpha$) level so that you can calculate 90% Confidence Interval.__

Type your answer here.


__Question 8.5.3. Calculate t statistic and explain what you see in the output.__

```{r}

# Type your codes here

```


Type your answer here.


__Question 8.5.4. Explain what each function/argument does in this question.__

`t_test`: Type your answer here.

`formula`:Type your answer here.

`order`: Type your answer here.

`alternative`: Type your answer here.

`conf.level`: Type your answer here.

`var.equal`: Type your answer here.


__Question 8.5.5. Draw a conclusion and write a conclusion statement. Include your comment on 90% Confidence Interval.__


Type your answer here.


## Paired Samples _t_ test

__Example of a Case:__ Pollutants in a stream may accumulate or attenuate as water flows down the stream. In a study to monitor the accumulation and attenuation of fecal contamination in a stream running through cattle rangeland, monthly water specimens were collected at two locations along the stream over a period of 21 months.

The data set `stream` the total coliform count (MPN/100ml) for a water specimen.

__Question 9.1. What is the research question of this study?__


Type your answer here.


__Question 9.2. What type of variables do we have in this study?__


Type your answer here.


__Question 9.3. Please list the assumptions required for this test and check the assumption of normality for this study. Interpret the assumptions overall.__


_Random Sampling:_ Explain here.

_Independence of Observation:_ Explain here.

_Normal Distribution:_ Explain here.


Type your overall reasoning here.


__Question 9.4. Perform a paired samples $t$-test to assess whether the mean total coliform count is consistent across the two locations. Use the 5% significance level ($\alpha = 0.05$).__


Type your answer here.



__Question 9.5.1 Write out the null & the alternative hypothesis in words, in the context of this study:__

Type your answer here.


__Question 9.5.2. Determine \($\alpha$) level (Find it within the case given above).__

Type your answer here.


__Question 9.5.3. Calculate t statistic and explain what you see in the output.__

```{r}
# load the data set given and perform the test.
```


Type your answer here.


__Question 9.5.4: What is the difference between the two `t_test` functions in independent samples t test and paired samples t test?__


Type your answer here.


__Question 9.5.5: Draw conclusion and write a conclusion statement.__


Type your answer here.


## The Chi-Square for Goodness of Fit


__In this section, you are expected to write a case study based on your data set. In other words, choose a categorical variable and conduct a The Chi-Square for Goodness of Fit test. Show your work.__

__Question 10.1 Introduce your case study here.__

Type your case here.

__Question 10.2. What is the research question of this study?__


Type your answer here.


__Question 10.3. What type of variable do we have in this study?__


Type your answer here.


__Question 10.4. Please list the assumptions required for this test.__


Type your answer here.



__Question 10.5.1 Write out the null & the alternative hypotheses:__

Type your answer here.


__Question 10.5.2. Determine the \($\alpha$) level.__

Type your answer here.

__Question 10.5.3. Calculate Chi-square statistic and find the p-value and explain what you see in the output.__

```{r}

# Type your R Code here.

```

Type your answer here.


__Question 10.5.4. Compute expected counts for each cell. Interpret the assumptions overall that you listed in Question 10.4.__


```{r}

# Type your R Code here.

```

Type your answer here.  Interpret the assumptions overall and type your reasoning.

__Question 10.5.5. Draw conclusion and write a conclusion statement.__


Type your answer here.

