---
title: "Chi-Square Worksheet"
subtitle: "Week 7 Lecture 1 Lab 06"
format: pdf
---


# What is Chi-Square Test?


Type your lecture notes here.



# Chi-Square for Goodness of Fit


__When do we need to use this test:__ Type your lecture notes here.




__What type of variable(s) do we need to conduct this test:__ Type your lecture notes here.




__Research Question of this study:__ Type your lecture notes here.


__Table of the Case__

```{r}
#| echo: true
#| output: true
gss <- data.frame(
  Category = c("All 1000 get the drug", 
               "500 get the drug 500 don't"),
  n = c(99, 571)
)
print(gss)
```


## Steps for Conducting Hypothesis Testing for This Test


### Step 1. Formulate Hypotheses

_Write out the null & the alternative hypothesis:_

Type your lecture notes here.


### Step 2. Checking Conditions/Assumptions:

Type your lecture notes here.


### Step 3. Calculate Chi-square statistic and interpret the output



```{r}
gss_observed <- c(99, 571)
expected_proportions <- c(0.2, 0.8)
chisquare_gof <- chisq.test(gss_observed, p = expected_proportions)
chisquare_gof
```

Type your lecture notes here.


### Go back to Step 2. Checking Conditions/Assumptions:

Check expected counts for each cell.

```{r}
#| echo: true
#| output: true
chisquare_gof$observed
```

```{r}
#| echo: true
#| output: true
chisquare_gof$expected
```

Type your lecture notes here.


### Step 4. Draw conclusion



__Conclusion Statement:__


Type your lecture notes here.




# Chi Square Test for Independence 



__When do we need to use this test:__ Type your lecture notes here.




__What type of variable(s) do we need to conduct this test:__ Type your lecture notes here.




__Research Question of this study:__ Type your lecture notes here.


__Table of the Case__

```{r}
#| echo: true
#| output: true

# We create a 2 by 2 table
table_data <- matrix(c(69, 36, 454, 226), nrow = 2)

# We convert it to a data frame
concern_gw <- as.data.frame(table_data)

# We add meaningful column and row names
colnames(concern_gw) <- c("Duke", "US")
rownames(concern_gw) <- c("A Great Deal", "Not A Great Deal")

print(concern_gw)

```

## Steps for Conducting Hypothesis Testing for This Test

### Step 1. Formulate Hypotheses

_Write out the null & the alternative hypothesis:_

Type your lecture notes here.


### Step 2. Checking Conditions/Assumptions:

Type your lecture notes here.


### Step 3. Calculate Chi-square statistic and interpret the output



```{r}
#| echo: true
#| output: true
chi_square_result <- chisq.test(concern_gw)
print(chi_square_result)

```

Type your lecture notes here.



### Go back to Step 2. Checking Conditions/Assumptions:

Check expected counts for each cell.

```{r}
#| echo: true
#| output: true
chi_square_result$observed
```

```{r}
#| echo: true
#| output: true
chi_square_result$expected
```

Type your lecture notes here.


##
### Step 4. Draw a Conclusion!

__Conclusion Statement:__ Type your lecture notes here.
