---
title: "STAT 218 Lab Assignment 2"
author: 
  - "Team Member 1: NAME HERE"
  - "Team Member 2: NAME HERE"
  - "Team Member 3: NAME HERE"
date: today
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: pdf
execute:
  echo: true
---


## Lab Assignment 2

In this assignment, we will work with the data available in the package of `palmerpenguins`. Let's install and use that package. And let's load our data into R by using `data()` function.

Run the code chunk below. __DO NOT FORGET TO RENDER YOUR QUARTO DOCUMENT TO PDF!__

```{r}
#| include: false
install.packages("palmerpenguins" , repos = "http://cran.us.r-project.org")
library(palmerpenguins)
data("penguins") 
```

__NOTE:__ Please ignore `penguins_raw` data for this class and USE `penguins` for this assignment.

__Question 1: Please use `glimpse()`function and write 2-3 sentences to explain what you see.__


```{r}

# Put your R Code Chunk here. 

```


Type your answer (2-3 sentences) here.


__Question 2: How many variables and cases do this dataset have?__

```{r}

# Put your R Code Chunk here. 

```


Type your answer here.


__Question 3: What types of variables are there in this data set? Identify each variable below (nominal, ordinal, discrete, and continuous?__

__species:__

__island:__

__bill_length_mm:__

__bill_depth_mm:__

__flipper_length_mm:__

__sex:__

__year:__


__Question 4: Calculate the mean and median values for `bill_lenght_mm__.

```{r}

# Put your R Code Chunk here. 

```

__Question 5: Please create a bar chart by using `ggplot()` function for the variable `species`.__

```{r}

# Put your R Code Chunk here.

```
