---
title: "STAT 218 Lab Assignment 5"
author: 
  - "Team Member 1: NAME HERE"
  - "Team Member 2: NAME HERE"
  - "Team Member 3: NAME HERE"
  - "Team Member 4: NAME HERE "
  - "Team Member 5: NAME HERE "

date: today
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: pdf
execute:
  echo: true
---

## Lab Assignment 5


__Directions:__ As usual, let's use `library` function and load the data set that we will use today.

```{r}
#| output: false
library(tidyverse)
library(infer)
library(palmerpenguins)
data("penguins")
```

__NOTE:__ Please ignore `penguins_raw` data for this class and USE `penguins` for this assignment.




# Chi-Square for Goodness of Fit

  
__Example of a Case:__ Imagine that you are a biologist studying penguins, particularly interested in whether the proportion of female penguins differs significantly from 50%?. Assume that you collect a random sample of 344 penguins.



__Question 1. What is the research question of this study?__


Type your answer here.


__Question 2. What type of variable do we have in this study?__


Type your answer here.


__Question 3. Please list the assumptions required for this test.__


Type your answer here.



__Question 4.1 Write out the null & the alternative hypotheses:__

Type your answer here.


__Question 4.2. Calculate Chi-square statistic and find the p-value and explain what you see in the output.__

```{r}

# Type your R Code here.

```

Type your answer here.


__Question 4.3. Compute expected counts for each cell. Interpret the assumptions overall that you listed in Question 3.__


```{r}

# Type your R Code here.

```

Type your answer here.  Interpret the assumptions overall and type your reasoning.

__Question 4.4. Draw conclusion and write a conclusion statement.__


Type your answer here.



# Chi Square Test for Independence 

  
__Example of a Case:__ Now, you're curious about whether the proportion of species differ in different islands.


__Question 1. What is the research question of this study?__


Type your answer here.


__Question 2. What type of variables do we have in this study?__


Type your answer here.


__Question 3. Please list the assumptions required for this test.__


Type your answer here.



__Question 4.1 Write out the null & the alternative hypothesis:__

Type your answer here.




__Question 4.2. Calculate Chi-square statistic and find the p-value and explain what you see in the output.__


You need a package to run this code. Don't forget to remove # and then add it back. Otherwise, you cannot render your PDF document.

```{r}
# install.packages("janitor")
```

```{r}
#| warning: false
library(janitor)

# Create a contingency table for your analysis
contin_table <- penguins %>%
  tabyl(island, species)

contin_table

```
Now conduct your chi-square test

```{r}
# Conduct the chi-square test by using `contingency_table`
```



Type your answer here.



__Question 4.3. Compute expected counts for each cell. Interpret the assumptions overall that you listed in Question 3.__


```{r}

# Type your R Code here.

```

Type your answer here. Interpret the assumptions overall and type your reasoning.


__Question 4.4. Draw conclusion and write a conclusion statement__


Type your answer here.


