--- 
title: "Data Visualization with ggplot()"
subtitle: "STAT 218 Lab Worksheet"
author: Your Name
date: today
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: pdf
execute:
  echo: true
---


:::{.callout-warning}
We will learn how to visualize our data set today. You do not need to memorize these codes in this lecture. Please try to understand these conceptually.
:::

  
## Data Visualizations

Visuals are graphical representations of data. We use different colors, shapes, and the coordinate system to (1) summarize data; (2) tell a story or (3) explore data before conducting inferential statistics.


Let's start with loading today's data set by using `library()`, `data()`, and `glimpse()`function to start.


```{r}
#| message: false
#| warning: false
library(tidyverse)
library(openintro)
data(babies)
babies <- babies %>% 
  mutate(smoke = as.logical(smoke),
         parity = as.logical(parity))
```

Before starting, let's have a look our data and variable types by using `glimpse()`function

```{r}
# Put your glimpse function here
```



Let's use ? to get more info

```{r}
? babies
```

You can see the info below in your Help tab.


`case`: id number

`bwt`: birth weight, in ounces

`gestation`: length of gestation, in days

`parity`: binary indicator for a first pregnancy (0 = first pregnancy)

`age`: mother's age in years

`height`: mother's height in inches

`weight`: mother's weight in pounds

`smoke`: binary indicator for whether the mother smokes

 
## Visualizing a Single Categorical Variable

Let's choose one categorical variable and try to produce a bar plot


```{r}

# Put your R Code here to produce a bar chart

```

 

## Visualizing a Single Numeric Variable

Let's use `bwt` variable which is a numeric variable indicating birth weight in ounces. Choose your color from this [link](https://www.stat.auckland.ac.nz/~ihaka/downloads/R-colours-a4.pdf)
 
```{r}

# Put your R Code here to produce a histogram

```

### English

- Create a ggplot using the babies data frame.
- Map the `bwt` to the x-axis.
- Add a layer of a histogram.
- Change the binwidth to 15.
- Color the borders of the bars (bins?) as white.
- Fill it with a color code named maroon

### R Code

```{r}
#| output: false
ggplot(data = babies,
       aes(x = bwt)) +
  geom_histogram(binwidth = 15, 
                 color = "white", 
                 fill = "maroon")
```

### Plot

```{r}
#| echo: false
ggplot(data = babies,
       aes(x = bwt)) +
  geom_histogram(binwidth = 15, 
                 color = "white", 
                 fill = "maroon")
```


 

## Visualizing Two Categorical Variables 

Now we will try to fill the y-axis as if it is something look like percentage which is called __Standardized Bar Plot__. Note that y-axis is no longer count but we will learn how to change that later.

```{r}

# Put your R Code here to produce a standardized bar plot

```


 

## Visualizing One Categorical and One Numeric Variable

We are visualizing a single numerical (`bwt`) and single categorical variable (`smoke`) by using `geom_boxplot`

```{r}

# Put your R Code here to produce a box plot

```

 

## Visualizing Two Numeric Variables 

We are visualizing two numerical (`bwt` & `gestation`) by using `geom_point`

```{r}

# Put your R Code here to produce a scatterplot

```

 

## Visualizing More than Two Variables 

We are visualizing two numerical (`bwt` & `gestation`) and one categorical (`smoke`) variables 

```{r}

# Put your R Code here

```
 




