---
title: "STAT 218 Lab Assignment 3"
author: 
  - "Team Member 1: NAME HERE"
  - "Team Member 2: NAME HERE"
  - "Team Member 3: NAME HERE"
  - "Team Member 4: NAME HERE"
  - "Team Member 5: NAME HERE"
date: today
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: pdf
execute:
  echo: true
---


## Lab Assignment 1

In this assignment, we will work with the data available in the package of `palmerpenguins`. Please install and use that package if did not do it so far. 

And let's load our data into R by using `data()` function.

```{r}
#| include: false
library(palmerpenguins)
data("penguins") 
```

__NOTE:__ Please ignore `penguins_raw` data for this class and USE `penguins` for this assignment.

__Question 1: Please use `glimpse()`function and write 2-3 sentences to explain what you see.__


```{r}

# Put your R Code Chunk here. 

```


Type your answer (2-3 sentences) here.


__Question 2: Choose a numeric variable and create a histogram to visualize it. Provide an explanation of the observed distribution.__

```{r}

# Put your R Code Chunk here. 

```


Describe the patterns and insights you observe in the histogram.




__Question 3: Create a boxplot by using the variables `species` and `bill_length_mm`. Describe the graph using your own words.__


```{r}

# Put your R Code Chunk here. 

```


__Question 4: Using the `geom_point()` function, plot a graph that shows the linear relationship between `bill_length_mm` and `bill_depth_mm`, coloring different `species` in that graph.__

```{r}

# Put your R Code Chunk here. 

```


